\chapter{Introduction}
\label{c:intro}

The standard model (SM) of particle physics is the currently accepted theory for describing the known fundamental building blocks of the universe. It includes the six quarks and six leptons (and their anti-particles), and the four fundamental forces, electromagnetism, weak force, strong force and gravity. It also includes the Higgs boson that arises from the Brout-Englert-Higgs mechanism, which describes the origin of mass of the quarks, leptons and weak gauge bosons.
It has stood up to rigorous testing at experiments such as at the Deutsches Elektronen-Synchrotron (DESY), the Large Electron Positron collider (LEP) at CERN and the Tevatron at Fermilab. However there are still many unanswered questions about the universe such as how does gravity fit in when it is not described in the SM? What is the dark matter in the universe that affects galaxy rotation curves and causes gravitational lensing where no baryonic matter is present. 
The Large Hadron Collider (LHC) at CERN aims to answers these question by studying the possible signatures of new physics that may arise around the electroweak scale. One of the main goals of the LHC was to find the Higgs boson which was confirmed in July 2012. The precision measurement of SM processes is also still very important as deviations from the SM expectation can give hints about new physics and they are also key background processes which should be well understood so that new physics signals can be found.

The SM process of the production of four top quarks is studied in this thesis. Although this process is predicted by the SM, it is extremely rare and hence it has not yet been possible to measure it. A precision measurement of four top quark production would be an exceptional test of the SM. In addition to this, many models of new physics predict final states which contain four top quarks including supersymmetry, models with extra dimensions, models where the top quark/Higgs boson is a composite particle, or models which contain pair-produced scalar particle which decay into top quark pairs.
Therefore the SM production of four top quarks is both an important background to these new models and the production rate of four top quarks may be enhanced by new physics models.

The thesis is structured as follows: First the background theory of particle physics and top quark physics is discussed in Chapter~\ref{c:theory}. The LHC and particularly the CMS detector are described in Chapter~\ref{c:det}. The reconstruction of physics objects from the detector read-out are given in Chapter~\ref{c:recon}. In Chapter~\ref{c:ana} the general strategy for searching for four top quarks and the analytical and statistical techniques required are described. The search for four top quarks in the single lepton channel in the 2012 dataset collected by the CMS experiment at $\sqrt{s}=8$~TeV is described in Chapter~\ref{c:Run1}. The phenomenological interpretation of the former analysis and another CMS same-sign dilepton analysis in the context of a model of new physics where a sgluon particle is predicted is given in Chapter~\ref{c:pheno}. The search for four top quarks is continued in the 2015 dataset collected by the CMS experiment at $\sqrt{s}=13$~TeV, described in Chapter~\ref{c:Run2}, where enhancements are made to the analysis and additional search channels, opposite-sign and same-sign dilepton are combined with the single lepton channel to produce a more sensitive final result. Finally a summary of the thesis can be found in Chapter~\ref{c:DandC}, including a discussion of the relevance of the analysis in the field of high energy physics and a look towards the future.

The author's personal contributions to the analyses in this thesis include: 
\begin{itemize}
\item In Chapter~\ref{c:Run1}, on the search for four top quarks at $\sqrt{s}=8$~TeV, Sections~\ref{sec:QCDbackground},~\ref{sec:njetcatlimit} and~\ref{studies8}.
\item All of the work in Chapter~\ref{c:pheno}, except on Figure~\ref{fig:sgluonExclusion}, the result from the single lepton channel was not the author's work.
\item In Chapter~\ref{c:Run2}, on the search for four top quarks at $\sqrt{s}=13$~TeV, all sections except for the training of the hadronic top BDT in Section~\ref{sec:topContent13} are the author's work.
\end{itemize}


In this thesis the convention of using natural units, $\hbar = c = 1$, is adopted. 
