\chapter*{Acknowledgements} 

First of all I would like to thank my supervisors, Freya Blekman and Joel Goldstein, for being incredibly supportive, helpful and great fun to work with over the past four years. I would also like to thank James Keaveney for teaching me everything possible about being a four-top expert in the first two years of my PhD, for continuing to discuss physics problems with me since then and for being great craic. It was also a pleasure to work with Jesse and Steve from UCR on combining our four-top searches together and I wish Denys and Long the best in taking the analysis forward from here.
I would like to thank my collaborators on our phenomenology project, Didar, Benjamin and Kentarou, for a fruitful and interesting collaboration. I would like to thank both the Bristol and Brussels research group for being great colleagues and fun to work with. I would particularly like to thank Robin for all the advice, memes and the exchange of swearing at pieces of code, and Maarten for housing and feeding me at the very start of my PhD while I found somewhere to live. Many thanks go to Martisse, you are sunshine on a cloudy day. 
Thanks to Leonor for being a supportive flatmate over this past two years and helping me out in these last few weeks of writing. Thanks to Mark for being my rock, for encouraging me and helping me through this writing period and for always being there to laugh with me.
I am incredibly appreciative of the never-ending support from my parents who brought me up to believe that I could be whatever I wanted to be.

Lastly, of course, this thesis would not be possible without the work from everyone in the CMS collaboration who work together for the common goal of pushing the boundaries of physics.

